---
output: html_document
---

#### **To:** The museum board of directors  
  
#### **From:** Mengyao Zhang  
  
#### **Date:** `r format(Sys.time(), '%B %d, %Y')`   
  
#### **RE:** Analysis of the proposals for Exhibit  

***


```{r echo = FALSE, message = FALSE, warning = FALSE}
# Title: Artie's Dream Proposal 1-3
# Purpose: Provide the solution for proposal 1-3
# Date: June 10, 2018
# Author: Mengyao Zhang
```

 
```{r echo = FALSE, message = FALSE, warning = FALSE, results = "hide"}
# Clear packages 
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(
  paste("package:", names(sessionInfo()$otherPkgs), sep=""), 
  detach, character.only = TRUE, unload = TRUE)

# Clear environment
rm(list = ls(all = TRUE)) 

```


```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load librarys
library(knitr) # For making a nice table, there are options to make nicer tables
library(lpSolveAPI)
library(kableExtra)
library(dplyr)
#reads all data from the excel file
dat <- read.csv("5260_S18_Arties_Dream.csv",header = TRUE,stringsAsFactors = FALSE,fileEncoding="latin1") 
```

### Introduction

As you all know, Artie Fophartie decided to use his own money to fund an exhibit of up-and-coming modern artists at the Seattle Museum of Modern Art. The success of this exhibition will benefit not only the artists but also the citizens. Currently, there are 34 pieces of art available but considering the limited budget and spaces, only part of them could be displayed. In addition, Artie and Celeste, as the sponor and the museum director, respectively, possess their requiements and agenda for this exhibit. 

To ensure the success of the exhibition, as an analyst, I analyze three proposals and 
find out the optimal solutions that meet both Artie and Celeste's requirments. The three proposals are:   
1) Maximize the number of pieces displayed within $4 million budget;   
2) Minimize the cost including at least 20 pieces;   
3) The impact on proposal 2 if the cost of each piece randomly change between –20% and +20%.

***
### Solution for proposal 1: Maximaze the number of pieces


```{r, include=FALSE}
# rename two columns 
colnames(dat)[colnames(dat)=="Price...1000."] <- "Price"
colnames(dat)[colnames(dat)=="Artist..Piece"] <- "Artist_Piece"

# remove the symbols from column "Piece"
dat$Piece <- gsub("\u0093","",dat$Piece)
dat$Piece <- gsub("\u0094","",dat$Piece)
```

```{r,include=FALSE}
# define constraint matrix
mat1 <- matrix(rep(0,length = 850),nrow = 25,ncol = 34)
colnames(mat1) <- c(1:34)

# 1) set budget constraint
for (i in 1:34){
  colnames(mat1)[i] <- dat[i,1]
  mat1[1,i] <- dat[i,"Price"]
}

# 2) set "only one collage" constraint
for (i in grep("collage",dat$Description)) {
  mat1[2,i] <- 1
}

# 3-7) set "wire mesh if computer-generated" constraint
for (i in grep("wire mesh",dat$Description)) {
  mat1[3,i] <- -1
  mat1[4,i] <- -1
}
for (i in grep("computer-generated",dat$Description)[1]) {
  mat1[3,i] <- 1
}
for (i in grep("computer-generated",dat$Description)[2]) {
  mat1[4,i] <- 1
}

for (i in grep("wire mesh",dat$Description)[1]) {
  mat1[5,i] <- 1
}
for (i in grep("wire mesh",dat$Description)[2]) {
  mat1[6,i] <- 1
}
for (i in grep("wire mesh",dat$Description)[3]) {
  mat1[7,i] <- 1
}
for (i in grep("computer-generated",dat$Description)) {
  mat1[5,i] <- -1
  mat1[6,i] <- -1
  mat1[7,i] <- -1
}



# 8) set "photo-realistic" constraint
for (i in grep("photo-realistic",dat$Description)) {
  mat1[8,i] <- 1
}
# 9) set "cubist paint" constraint
for (i in grep("cubist",dat$Description)) {
  mat1[9,i] <- 1
}
# 10) set "watercolor" constraint
for (i in grep("water",dat$Description)) {
  mat1[10,i] <- 1
}
# 11) set "oil paint" constraint
for (i in grep("oil",dat$Description)) {
  mat1[11,i] <- 1
}
# 12）set "expressionist" constraint
for (i in grep("expressionist",dat$Description)) {
  mat1[12,i] <- 1
}


# 13) set "painting < 2 times of other forms" constraint
for (i in grep("painting",dat$Description)) {
  mat1[13,i] <- 1
}
for (i in grep("collage|drawing|sculpture",dat$Description)) {
  mat1[13,i] <- -2
}

# 14) set "all Artie & all Helen's painting" constraint
for (i in grep("Artie|Helen",dat$Artist)) {
  mat1[14,i] <- 1
}
# 15) set "David >= 1" constraint
for (i in grep("David",dat$Artist)) {
  mat1[15,i] <- 1
}
# 16) set "Ziggy >= 1" constraint
for (i in grep("Ziggy",dat$Artist)) {
  mat1[16,i] <- 1
}
# 17) set "David = Ziggy " constraint
for (i in 1:ncol(mat1)) {
  if(dat[i,"Artist"]=="David Lyman"){
    mat1[17,i] <- 1
  }else if (dat[i,"Artist"]=="Ziggy Stardust") {
    mat1[17,i] <- -1  
  }else {
    mat1[17,i] <- 0  
    }
}

# 18) set "Rick <= 1 " constraint
for (i in grep("Rick",dat$Artist)) {
  mat1[18,i] <- 1
}

# set Celeste's constraints in matrix
# 19) Female >= 1/2 Male
for (i in 1:ncol(mat1)) {
  ifelse(dat[i,"Gender"]=="F", mat1[19,i]<-2, mat1[19,i]<- -1)
}
```


```{r,include=FALSE}
# 20) 'Aging earth" or/and "wasted resources"
for (i in grep("Aging Earth|Wasted Resources",dat$Piece)) {
  mat1[20,i] <- 1
}
# 21) at least one piece by Bear Canton
for (i in grep("Bear",dat$Artist)) {
  mat1[21,i] <- 1
}
# 22) at least one of the following pieces:“Beyond,” “Who Has Control,” “Where are we now?” and “Pioneers.”
for (i in grep("Beyond|Who Has Control|Where are we now?|Pioneers",dat$Piece)) {
  mat1[22,i] <- 1
}

# 23) limited space for scupture
for (i in grep("sculpture",dat$Description)) {
  mat1[23,i] <- 1
}
# 24) limited space for collage + drawing + painting
for (i in grep("collage|drawing|painting",dat$Description)) {
  mat1[24,i] <- 1
}
# 25)  if “Narcissism” is displayed, then “Reflection” display
for (i in 1:ncol(mat1)) {
  if(dat[i,"Piece"]=="Narcissism"){
    mat1[25,i] <- 1
  }else if (dat[i,"Piece"]=="Reflection") {
    mat1[25,i] <- -1  
  }else {
    mat1[25,i] <- 0  
    }
}
```


```{r,include=FALSE}
# Set up maximize the number of pieces with BIP
p1_bip <- make.lp(0, 34)

# Set up model
obj_fn <- rep(1,length = 34)
set.objfn(p1_bip, obj_fn)

# set constraints by Artie
add.constraint(p1_bip, mat1[1,], "<=", 4000)  # 1)budget <= 4M
add.constraint(p1_bip, mat1[2,], "=", 1)      # 2)only one collage

# 3-7) at least one wire mesh if has computer-generated
for (i in 3:7){
add.constraint(p1_bip, mat1[i,], "<=", 0) 
}

# 8-12)at least one photo-realistic,one cubist,one watercolor,one oil painting,one expressionist
for (i in 8:12) {
add.constraint(p1_bip, mat1[i,], ">=", 1)    
}

add.constraint(p1_bip, mat1[13,], "<=", 0)     # 13) painting < 2 times of other forms
add.constraint(p1_bip, mat1[14,], "=", sum(mat1[14,])) # 14) all Artie & Helen's painting are displayed
add.constraint(p1_bip, mat1[15,], ">=", 1)     # 15) David >= 1
add.constraint(p1_bip, mat1[16,], ">=", 1)     # 16) Ziggy >= 1
add.constraint(p1_bip, mat1[17,], "=", 0)      # 17) David = Ziggy 
add.constraint(p1_bip, mat1[18,], "<=", 1)     # 18) Rick <= 1

# set constraints by Celeste
add.constraint(p1_bip, mat1[19,], ">=", -1)    # 19) 2*Female - Male >= -1
add.constraint(p1_bip, mat1[20,], ">=", 1)     # 20)"Aging earth" or/and "wasted resources"
add.constraint(p1_bip, mat1[21,], ">=", 1)     # 21) Bear >= 1
add.constraint(p1_bip, mat1[22,], ">=", 1)     # 22) at least one of the four pieces: beyond...
add.constraint(p1_bip, mat1[23,], "<=", 4)     # 23) sculpture <= 4
add.constraint(p1_bip, mat1[24,], "<=", 20)    # 24) other forms of art <= 20
add.constraint(p1_bip, mat1[25,], "<=", 0)     # 25) if “Narcissism”  then “Reflection” 

# Set the type "binary" of each decision variable
for (i in 1:34) {
  set.type(p1_bip, i, "binary")
}
# Solve the model, if this return 0 an optimal solution is found
solve(p1_bip)
```


```{r, echo= FALSE, include=FALSE}
get.objective(p1_bip)
get.solutioncount(p1_bip)
get.variables(p1_bip) 
```

There are at most 15 pieces shown as below could be displayed, with the total cost of $3.95 million dollars.  

```{r echo=FALSE}
# Generate the solution1 table
result1 <- vector()
for (i in 1:34) {
  if(get.variables(p1_bip)[i] == 1) {
    result1 <- rbind(result1, c(i, unlist(dat[i,-1], use.names = FALSE)))
  } else {next
    }
}
colnames(result1) <- c(" ", colnames(dat[-1]))

kable(result1, format = "html") %>%
  kable_styling("striped")
```

***
### Solution for proposal 2: Minimize the Cost

```{r,include=FALSE}
# 1) adjust the first row of matrix
for (i in 1:34){
  mat1[1,i] <- 1
}
# Set up maximize the number of pieces with BIP
p1_bip <- make.lp(0, 34)
# Set up model
obj_fn <- dat[,"Price"]
set.objfn(p1_bip, obj_fn)

# set constraints by Artie
add.constraint(p1_bip, mat1[1,], ">=", 20)    # 1) at least 20 pieces
add.constraint(p1_bip, mat1[2,], "=", 1)      # 2) only one collage

# 3-7) at least one wire mesh if has computer-generated
for (i in 3:7){
add.constraint(p1_bip, mat1[i,], "<=", 0) 
}

# 8-12)at least one photo-realistic,one cubist,one watercolor,one oil painting,one expressionist
for (i in 8:12) {
add.constraint(p1_bip, mat1[i,], ">=", 1)    
}

add.constraint(p1_bip, mat1[13,], "<=", 0)     # 13) painting < 2 times of other forms
add.constraint(p1_bip, mat1[14,], "=", sum(mat1[14,])) # 14) all Artie & Helen's painting are displayed
add.constraint(p1_bip, mat1[15,], ">=", 1)     # 15) David >= 1
add.constraint(p1_bip, mat1[16,], ">=", 1)     # 16) Ziggy >= 1
add.constraint(p1_bip, mat1[17,], "=", 0)      # 17) David = Ziggy 
add.constraint(p1_bip, mat1[18,], "<=", 1)     # 18) Rick <= 1

# set constraints by Celeste
add.constraint(p1_bip, mat1[19,], ">=", -1)    # 19) 2*Female - Male >= -1
add.constraint(p1_bip, mat1[20,], ">=", 1)     # 20)"Aging earth" or/and "wasted resources"
add.constraint(p1_bip, mat1[21,], ">=", 1)     # 21) Bear >= 1
add.constraint(p1_bip, mat1[22,], ">=", 1)     # 22) at least one of the four pieces: beyond...
add.constraint(p1_bip, mat1[23,], "<=", 4)     # 23) sculpture <= 4
add.constraint(p1_bip, mat1[24,], "<=", 20)    # 24) other forms of art <= 20
add.constraint(p1_bip, mat1[25,], "<=", 0)     # 25) if “Narcissism”  then “Reflection” 

# Set the type "binary" of each decision variable
for (i in 1:34) {
  set.type(p1_bip, i, "binary")
}
# Solve the model, if this return 0 an optimal solution is found
solve(p1_bip)
```


```{r, include=FALSE}
solve(p1_bip)
get.objective(p1_bip)
get.solutioncount(p1_bip)
get.variables(p1_bip) 
```

To including at least 20 pieces, the table below shown the pieces could be displayed. There are exact 20 pieces been selected at the minimum cost of $5.45 million dollars.

```{r echo=FALSE}
# Generate random variables for a table
result2 <- vector()
for (i in 1:34) {
  if(get.variables(p1_bip)[i] == 1) {
    result2 <- rbind(result2, c(i, unlist(dat[i,-1], use.names = FALSE)))
  } else {next
    }
}
colnames(result2) <- c(" ", colnames(dat[-1]))
kable(result2, format = "html") %>%
  kable_styling("striped")
```

***

### Solution for proposal 3:
```{r,include=FALSE}
set.seed(1234)

total_cost <- vector()
n <- 1000
for (i in 1:n) {
dat$change <- round(runif(34,0.8,1.2),2)
dat$new_price <- dat$Price * dat$change
# Set up maximize the number of pieces with BIP
p1_bip <- make.lp(0, 34)
# Set up model
obj_fn <- dat[,"new_price"]
set.objfn(p1_bip, obj_fn)

# set constraints by Artie
add.constraint(p1_bip, mat1[1,], ">=", 20)    # 1) at least 20 pieces
add.constraint(p1_bip, mat1[2,], "=", 1)      # 2) only one collage

# 3-7) at least one wire mesh if has computer-generated
for (i in 3:7){
add.constraint(p1_bip, mat1[i,], "<=", 0) 
}

# 8-12)at least one photo-realistic,one cubist,one watercolor,one oil painting,one expressionist
for (i in 8:12) {
add.constraint(p1_bip, mat1[i,], ">=", 1)    
}

add.constraint(p1_bip, mat1[13,], "<=", 0)     # 13) painting < 2 times of other forms
add.constraint(p1_bip, mat1[14,], "=", sum(mat1[14,])) # 14) all Artie & Helen's painting are displayed
add.constraint(p1_bip, mat1[15,], ">=", 1)     # 15) David >= 1
add.constraint(p1_bip, mat1[16,], ">=", 1)     # 16) Ziggy >= 1
add.constraint(p1_bip, mat1[17,], "=", 0)      # 17) David = Ziggy 
add.constraint(p1_bip, mat1[18,], "<=", 1)     # 18) Rick <= 1

# set constraints by Celeste
add.constraint(p1_bip, mat1[19,], ">=", -1)    # 19) 2*Female - Male >= -1
add.constraint(p1_bip, mat1[20,], ">=", 1)     # 20)"Aging earth" or/and "wasted resources"
add.constraint(p1_bip, mat1[21,], ">=", 1)     # 21) Bear >= 1
add.constraint(p1_bip, mat1[22,], ">=", 1)     # 22) at least one of the four pieces: beyond...
add.constraint(p1_bip, mat1[23,], "<=", 4)     # 23) sculpture <= 4
add.constraint(p1_bip, mat1[24,], "<=", 20)    # 24) other forms of art <= 20
add.constraint(p1_bip, mat1[25,], "<=", 0)     # 25) if “Narcissism”  then “Reflection” 

# Set the type "binary" of each decision variable
for (i in 1:34) {
  set.type(p1_bip, i, "binary")
}
# Solve the model, if this return 0 an optimal solution is found
solve(p1_bip)

total_cost <- rbind(total_cost, get.objective(p1_bip))
}

result_cost <- round(rbind(mean(total_cost), sd(total_cost),max(total_cost), min(total_cost)), 2)
colnames(result_cost) <- 'Total Cost ($1000)'
rownames(result_cost) <- c('mean','standard diviation', "max", "min")
result_cost
```

From the solution for proposal 2, the cost is $5.45 million. While after the randomly changing of the cost of each piece between -20% and +20%, the mean value of the total cost becomes $5.403 million, which decreased by about $47,000 dollars. In addition, since the standard diviation is relatively low compared to the mean value, it means that other total cost are closed to the average cost. So we don't need to worry about the big change of the total cost that the changing of may generate。

```{r, echo=FALSE}
kable(result_cost, align = "c")
```


***

### Conclusion

Through the above analysis, I think this exhibition will be an amazing event because we included all forms of the art we have, such as photograph, painting, sculpture and so on. Besides, as thoughtful as Celeste is, many pieces from female artists and native Americans are included, which shows the respect and support to a diverse population of artists. Many pieces that reflect current issues are included, for example, "Wasted Resources" could appeal to the citizens for save the natrural resources. Hope you could approve these great exhibits.
  
 
   
   
        